Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut

### 2023-10-30 manuscript/manuscript.tex
add subsections to discussion

What are the main contributions again?

What are the limitations of this study?
One limitation lies in the availability and quality of data. This dataset does not have any 
data from years after 2020 which may serve to limit potential external validity considerations. 
There may also be variability in data collection methods and discrepancies in reporting standards 
leading to missing or incomplete data over the course of 4 years. Another limitation involves the scope 
of the study, focusing on specific counties in Connecticut may not fully capture nationwide disparities. 
Additionally, the research is limited to the factor parameters selected to investigate which  might not 
encompass all relevant social determinants affecting health outcomes.

What are worth pursuing further in the future?

>>>>

The results of the analysis shed light on the intricate relationships between county, race, and key 
variables such as median income, housing affordability, rehospitalization rates, food stamps usage, 
uninsured rates, and racial demographics. Understanding these correlations is vital in comprehending 
the socio-economic and racial disparities prevalent in the studied region.

\subsection{Median Income}
The disparity in median income across the four years highlights economic fluctuations, with 
2020 exhibiting the highest income levels. County-wise analysis indicates stark differences, 
particularly in County 1, which consistently outperforms others. This discrepancy in wealth signifies 
potential disparities in access to resources and opportunities, which can significantly impact health outcomes.

\subsection{Housing Affordability}
The stable trend in the percentage of renters spending 50 percent of their income on rent suggests a 
consistent challenge faced by residents across the years. County 1 and 5 facing significantly higher 
rates reflect housing affordability issues, possibly indicating economic strains experienced by residents in these areas.

\subsection{Rehospitalization Rates}
The absence of significant differences in rehospitalization rates by both county and year indicates 
a consistent healthcare landscape. However, it's crucial to explore the reasons behind this stability to identify 
potential factors contributing to the overall health system's effectiveness.

\subsection{Food Stamps Usage}
Counties 8, 2, and 5 having higher percentages of the population on food stamps imply economic challenges 
faced by residents in these regions. This data aligns with the housing affordability trends, suggesting a potential 
link between financial struggles and reliance on government assistance programs.

\subsection{Uninsured Rates}
County 1's consistently high uninsured rate points towards a significant healthcare accessibility issue, 
possibly linked to economic factors impacting insurance affordability. Year 3's (2019) lower uninsured rate signifies 
a positive change; understanding the policies or interventions during this period could offer valuable insights into 
effective healthcare reforms.

\subsection{Racial Disparities}
The racial demographics highlight disparities in various counties. County 3's higher percentage of white 
individuals, coupled with County 2, 5, and 1 having the highest black population, points to the need for
targeted interventions addressing racial health inequalities. These disparities might be indicative of 
historical, social, and economic factors influencing the healthcare experiences of different racial groups.

\subsection{Limitations}
One limitation lies in the availability and quality of data. This dataset does not have any 
data from years after 2020 which may serve to limit potential external validity considerations. 
There may also be variability in data collection methods and discrepancies in reporting standards 
leading to missing or incomplete data over the course of 4 years. Another limitation involves the scope 
of the study, focusing on specific counties in Connecticut may not fully capture nationwide disparities. 
Additionally, the research is limited to the factor parameters selected to investigate which  might not 
encompass all relevant social determinants affecting health outcomes.

\subsection{Future Directions}
These findings underscore the complex interplay between socio-economic status, race, and health outcomes. Addressing these disparities requires multifaceted interventions, including economic support, affordable housing initiatives, and targeted healthcare access programs. Future research should delve deeper into the root causes of these disparities, considering historical and systemic factors. Additionally, policy interventions and community-based programs should be designed to specifically target areas and populations facing the most significant challenges, aiming for a more equitable healthcare landscape for all residents.
